### 2016-05-20 paper/intro.tex
added some notes on attempts to get rid of ridges; added option to use SUPG (which seems not to get rid of oscillations, even though oscillations seem related to Peclet number...)
Small additions.
added new figures (not yet made pretty) corresponding to new error breakdown for cd vs cdr case; added cost comparison (linear solve comparison)

Models that represent phenomena and processes can usually be organized in a hierarchy according to their fidelity and expense. The use of multiple models simultaneously for forward simulation is well established. In this work, we extend the use of the multi-fidelity models to inverse problems. We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest.

@@

\subsection{draft outline}
\bit 
\item background/previous work? to put this work in context?
\item mathematical formulation
  \bit
  \item define inverse problem and qoi
  \item derive error estimate
  \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
  \item relation to mesh refinement
  \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem? (Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
  \eit
\item numerical results (perhaps not include all of these...)
  \bit
  \item convection-diffusion(-reaction)
    \bit
    \item interpretation of error estimate breakdown (interaction of QoI with observations)
    \item large reaction term: MF model more cooperative with nonlinear solver
    \eit
  \item convection-diffusion-reaction, field vs scalar description of parameters
    \bit
    \item interface question: do we enforce continuity between the two models' parameters?
    \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
    \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
    \eit
  \item alternate/additional example: use setup from B+V? navier-stokes and another model? 
    \bit
    \item potential flow? model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
    \item there would still be the question of how to interface the models...
    \eit
  \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
  \eit
\item conclusion...what goes in this section usually? summary and directions for future work?
\eit

>>>>

Models that represent phenomena and processes can usually be organized in a hierarchy according to their fidelity and expense. The use of multiple models simultaneously for forward simulation is well established. In this work, we extend the use of the multi-fidelity models to inverse problems. We present a systematic method to use different constraints in different regions of the domain, while controlling the error due to the use of lower fidelity models in a target quantity of interest. Our approach is based on a novel use of adjoint error estimation, which enables the computation of third-order QoI error estimates, at the cost of solving an additional adjoint problem.

@@

\subsection{draft outline}
\bit 
\item background/previous work? to put this work in context?
  %this is probably enough? at least for previous work...
  %what context though? is this another way to approach inverse problems?
\item mathematical formulation
  \bit
  \item define inverse problem and qoi
  \item derive error estimate
  \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
  \item relation to mesh refinement
  \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem? (Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
    %solving for adjoint and forward simultaneously (KKT) might cause you to lose an order of accuracy?
    %where was that book that Oden might have mentioned inverse application of his method?
      %Multiscale methods : bridging the scales in science and engineering / edited by Jacob Fish. (TA335.M85 2010 in barker)
  \eit
\item numerical results (perhaps not include all of these...)
  \bit
  \item convection-diffusion(-reaction)
    \bit
    \item interpretation of error estimate breakdown (interaction of QoI with observations)
    \item large reaction term: MF model more cooperative with nonlinear solver
    \eit
  \item convection-diffusion-reaction, field vs scalar description of parameters
    \bit
    \item interface question: do we enforce continuity between the two models' parameters?
      %-navierstokes+stokes seems to require continuity of flux and velocity across boundary...?
      %-is it okay to mix diff and convdiff for the forward like we did? does the discontinuous velocity break any intergration-by-parts   assumptions? (no that's only if discontinuity in diffusion bit...)
    \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
    %alternative way to describe 'scalar' case? but here we say there is one scalar, so this would be how to combine them...if you wanted plateaus to be different, can let LF model be two-scalars...
    %fig 3.10 -> what does the inferred field look like? does it look like two different plateaus?
      % practice/T_channel/diff_param_res/with_reaction/long_channel_stash/qoi3_setup02_r4p2_deref/ (pushed 10/3/15)
        %at the very last refinement, most of refined region seems to be two large humps...and a section that looks pretty much like the surrounding scalar...so maybe 3 patches...
    \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
    \eit
  \item alternate/additional example: use setup from B+V? navier-stokes and another model? 
    \bit
    \item potential flow? model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
    \item there would still be the question of how to interface the models...(in stokes vs navier-stokes foward paper, they just required continuity of state variables (velocity field and presssure))
    %do scalar + field for infer BCs on BV NS thing? try for different QoIs? (can we have a variable live on a boundary while the rest are inside? vikram will poke roy about implementing)
    %stokes is good in slow flows...not in boundary layer cuz gradient is high...
    %what situation would it make sense to use the LF model in some place?
    \eit
  \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
  \eit
\item conclusion...what goes in this section usually? summary and directions for future work?
\eit

### 2016-05-20 paper/numerical_experiments.tex
added new figures (not yet made pretty) corresponding to new error breakdown for cd vs cdr case; added cost comparison (linear solve comparison)

\chapter{Numerical Results} \label{chap:results}

In this chapter we demonstrate some results from applying our approach to pairs of steady-state models, implemented using the \texttt{libMesh} library \cite{libMeshPaper}. In Section \ref{sec:cdvcdr}, we demonstrate the results using two models that differ in the physics modeled. In Section \ref{sec:constvfield}, the two models differ in the space to which the parameter belongs. In Section \ref{sec:costAnaly} we discuss the numerical costs of our approach.

%------------------------------------------------------------------------------%
\section{Convection-Diffusion and Convection-Diffusion-Reaction Models}  \label{sec:cdvcdr}
%------------------------------------------------------------------------------%

@@

Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error. Here we calculate the contribution to the estimated error by a particular element $\kappa$ by simply considering all area integrals in the error estimate expression, limited to that element. As described in Algorithm \ref{alg:refSeries}, based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$. In this case, once an element is assigned to the high-fidelity portion of the domain $\Omega_{HF}$, it remains assigned as such for all future subsequent mixed-fidelity models. Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}, while the effectivity index for the error estimate, defined by
\begin{equation}
\textrm{effectivity index}=\frac{\textrm{estimated QoI error}}{\textrm{true QoI error}},
\end{equation}
is shown in Figure \ref{fig:baseErrEff}.

It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate. In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $15\%$ of the domain.

\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF03_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF03.pdf}
    \vspace{-0.5\baselineskip}
    \caption{MF$_3$ ($15\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models.}
\label{fig:baseRef}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErrEff}
\end{figure}

\subsection{Interaction of Observations and QoI}

The element-wise decomposition of the error estimate (\ref{eq:finErrExp}) suggests the use of the high-fidelity model in areas of the domain where the parameter field is both informed by the observations and informative about the QoI. To see this, we compare the element-wise decomposition of the error estimate for three sizes of the QoI region $\Omega_I$ given the same set of observations, and for three sets of observations given the same QoI region. Again we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$. The element-wise decomposition of the error estimates (from the first three iterations) for the three sizes of the QoI region $\Omega_I$ given the same set of observations is shown in Figure \ref{fig:qoiStudy}, and for the three sets of observations given the same QoI region is shown in Figure \ref{fig:dataStudy}. For the three cases where the observations were fixed but the QoI region allowed to vary, more iterations were required as the QoI region expanded; only the first three iterations are shown in Figure \ref{fig:qoiStudy}. For the three cases where the QoI region was fixed but the set of observations allowed to vary, only three iterations were required to achieve an estimated absolute relative QoI error of less than $1\%$; all three iterations are shown in Figure \ref{fig:dataStudy}.

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.191\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/setup_5_3.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/setup_7_3.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/setup_3_3.pdf}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_LF.pdf}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF01.pdf}
    \caption{MF$_1$ \\ ($5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF02.pdf}
    \caption{MF$_2$ \\ ($10\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.243\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_qoi/qoi5_sens3/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi7_sens3/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_qoi/qoi3_sens3/err_breakdown_MF03.pdf}
    \caption{MF$_3$ \\ ($15\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same observations (teal points in (\subref{subfig:obsSetup})) and varying QoI region (purple box in (\subref{subfig:obsSetup})).}
  \label{fig:qoiStudy}
\end{figure}

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
  \begin{subfigure}[t]{0.191\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/setup_3_10.pdf}
    \includegraphics[width=\textwidth]{vs_data/setup_3_5.pdf}
    \includegraphics[width=\textwidth]{vs_data/setup_3_3.pdf}
    \caption{Locations of observations and QoI region $\Omega_I$}
    \label{subfig:obsSetup}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_LF.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_LF.pdf}
    \caption{MF$_0$ \\ ($0\%$ HF)}
    \label{subfig:obsLF}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF01.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF01.pdf}
    \caption{MF$_1$ \\ ($5\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.155\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF02.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF02.pdf}
    \caption{MF$_2$ \\ ($10\%$ HF)}
  \end{subfigure}
  \begin{subfigure}[t]{0.245\textwidth}
  \centering
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens10/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens5/err_breakdown_MF03.pdf}
    \includegraphics[width=\textwidth]{vs_data/qoi3_sens3/err_breakdown_MF03.pdf}
    \caption{MF$_3$ \\ ($15\%$ HF)}
    \label{subfig:obsMFlast}
  \end{subfigure}
  \caption{Compare the element-wise decomposition of the error estimates (\subref{subfig:obsLF}-\subref{subfig:obsMFlast}), given the same QoI region (purple box in (\subref{subfig:obsSetup})) and varying observations (teal points in (\subref{subfig:obsSetup})).}
  \label{fig:dataStudy}
\end{figure}

The convective aspect of the models causes information to flow with the velocity field, and the diffusive aspect causes information to spread locally. Thus, it is expected that it would be most important to use the high-fidelity model in the QoI region, and in areas around observations upstream and just downstream of the QoI region. Using the high-fidelity model around observations is expected to become less important as the observations are placed further downstream from the QoI region. These expectations are supported by the results. For this pair of models and a QoI that is the integral of the state over a region, an appropriate mixed-fidelity model could have been designed by intuition. However, the interaction between the observations and the QoI may not always be so intuitive, and it is in these cases that a rigorous method for forming a mixed-fidelity model would be most helpful.

%\subsection{Effect of Regularization} %removed; more regularization doesn't seem to imply you can stop refining sooner...

\subsection{Highly Nonlinear Problems} \label{sec:solveRob}

For a highly nonlinear high-fidelity model, it may sometimes be the case that solving the inverse problem requires a more complex or specialized optimization algorithm; for example, one may need to use continuation methods (such as in \cite{BaoLiu03}), or utilize a problem-specific preconditioner (such as in \cite{Hanke00}). However, solving the inverse problem with a mixed-fidelity model, where this high-fidelity model is only used in a small portion of the domain, may be achievable using a simpler optimization algorithm. In this subsection, we give an example of such a case.

To solve the inverse problem, we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search) to solve the optimality conditions of the corresponding optimization problem (see Equation \ref{eq:invOpt}). Keeping most of the setup described in Section \ref{sec:cdvcdrSetup}, we consider a different high-fidelity model, one where the magnitude of the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) is increased from $k_r=-42$ to $k_r=-442$; let this new model be denoted by HF$_{442}$. We can no longer simply use the default nonlinear solver in \texttt{libMesh} to solve the inverse problem with this new, more nonlinear high-fidelity model, as the solver fails to converge. Convergence can be achieved by using continuation; we solve the inverse problem for a sequence of models, varying the reaction coefficient in Equation (\ref{eq:cdvcdrHF}) from $k_r=-42$ to $k_r=-442$ at intervals of 50, and using the solution of one problem as the initial guess for the next.

Alternatively, we use Algorithm \ref{alg:refSeries} to generate a series of mixed-fidelity models using the low-fidelity model and the HF$_{442}$ model. The inverse problem can be solved for these mixed-fidelity models using the default nonlinear solver, and we are able to achieve an estimated relative QoI error of less than $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $25\%$ of the domain, as shown in Figure~\ref{fig:442Err}. Figure \ref{fig:442ErrEff} gives the effectivity index of the error estimates.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{442/err_est.pdf}
\caption{Estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
\label{fig:442Err}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{442/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model, with $k_r=-442$, is used.}
\label{fig:442ErrEff}
\end{figure}

%------------------------------------------------------------------------------%
\section{Constant versus Field Parameters}  \label{sec:constvfield}
%------------------------------------------------------------------------------%

In this section, we consider two models which differ in the space to which the parameter belongs. We first describe the problem setup, and then present results from applying our approach.

%------------------------------------------------------------%
\subsection{Problem Setup} %\label{sec:svfSetup}
%------------------------------------------------------------%

The high-fidelity model 
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
is again a single-species convection-diffusion-reaction equation with a nonlinear reaction term, where $k_d = 0.1$ is a diffusion coefficient and $k_r = -4.2$ is a reaction coefficient. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. Then the intermediate mixed-fidelity models have parameter fields which are non-constant in only portions of the domain. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The velocity field and boundary conditions, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in Section~\ref{sec:cdvcdr}. As the inverse problem is ill-posed, except for perhaps in the case where the low-fidelity model is used throughout the domain, regularization is added; the Tikhonov regularization term is $\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient. For this case, the domain is discretized by a regular mesh of quadrilaterals, with 15 and 75 elements along the short and long boundaries, respectively, for a total of 11,250 elements. The P\'{e}clet number never exceeds 0.34 in any part of the domain, so we do not require stabilization.

%------------------------------------------------------------%
\subsection{Adaptive Model Refinement} %\label{sec:svfBaseRef}
%------------------------------------------------------------%

Based on the element-wise decomposition of the estimated error, we increase the proportion of the domain in which the high-fidelity field representation model is used until the estimated absolute relative error in the QoI is less than $5\%$. In this case, we allow an element assigned to $\Omega_{HF}$ in one mixed-fidelity model to be reassigned back to $\Omega_{LF}$ in subsequent mixed-fidelity models if its contribution to the error is not large enough. Figure~\ref{fig:svfRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the first six of the series of mixed-fidelity models thus generated. The true and estimated absolute relative errors in the QoI for these same intermediate models are shown in Figure \ref{fig:svfErr}, while the effectivity index of the error estimate is shown in Figure \ref{fig:svfErrEff}.

\begin{figure}[h!]
\begin{subfigure}[b]{\textwidth}
\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_LF_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_0$ ($0\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF01_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_1$ ($5\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
  \centering
  \includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF02_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_2$ ($10\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF03.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_3$ ($12\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF04.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_4$ ($15\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF05.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_5$ ($20\%$ HF)}
  \vspace{0.8\baselineskip}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF06_divvy.pdf}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.pdf}
  \vspace{-0.7\baselineskip}
  \caption{MF$_6$ ($25\%$ HF)}
\end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion) for mixed-fidelity models.}
\label{fig:svfRef}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_eff.pdf}
\caption{Effectivity index of QoI error estimate, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErrEff}
\end{figure}

As in the previous example, the error estimates are only approximate due to the nonlinear term in both the low- and high-fidelity models. In this case, the high-fidelity model must also be used in a larger portion of the domain ($60\%$) before the estimated relative error in the QoI reaches the desired level.

%------------------------------------------------------------------------------%
\section{Cost Analysis} \label{sec:costAnaly}
%------------------------------------------------------------------------------%

In both the examples discussed in Sections \ref{sec:cdvcdr} and \ref{sec:constvfield}, the high-fidelity model is simple and solving the inverse problem with the high-fidelity model is easily achievable. Doing so actually requires less computational time than using Algorithm \ref{alg:refSeries} to rigorously form a mixed-fidelity model with which to solve the inverse problem instead. However, as discussed in Section \ref{sec:limits}, we assume in motivating our approach that solving the inverse problem with the high-fidelity model is prohibitively expensive; although there is no benefit, in terms of computational cost, to using our approach in the given examples, one would likely see such benefits for more complex models. Such a benefit is suggested in Section \ref{sec:solveRob}, where the inverse problem using the high-fidelity model is difficult to solve but our approach allows one to construct a mixed-fidelity model for which the inverse problem can be solved with a simple algorithm and yet produce a QoI with a small estimated relative error.

%can philosophically compare with chad's though, perhaps in param refinement, even though his is in parameter subspaces and ours is in physical space?

>>>>

\section{Numerical Experiments}
\red{Don't forget to trim figures and convert them to pdfs!}

\subsection{Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}

@@

Once the QoI error estimate is calculated using Equation (\ref{eq:finErrExp}), the error estimate is then localized to each element to give an element-wise decomposition of the error. As described in Algorithm \ref{alg:refSeries}, based on this element-wise decomposition, we increase the proportion of the domain in which the high-fidelity model is used until the estimated absolute relative error in the QoI is less than $1\%$. Figure \ref{fig:baseRef} shows the element-wise decomposition of the error estimate, as well as the subdomains where the low- and high-fidelity models are used, for the series of mixed-fidelity models thus generated. The true and estimated absolute relative errors in the QoI for these same mixed-fidelity models are shown in Figure \ref{fig:baseErr}.

It can be seen that in this case, while the error estimates are not exact due to the nonlinear reaction term in the high-fidelity model, the error estimates are fairly accurate. In addition, the QoI that would have been obtained from solving the inverse problem with the high-fidelity model can be replicated to within $1\%$ with a mixed-fidelity model where the high-fidelity model is used in only $10.5\%$ of the domain.

\begin{figure}[h!]
\centering
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_LF_divvy.pdf}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_LF.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_0$ ($0\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
	\begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF01_divvy.png}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF01.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_1$ ($5\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
  \begin{subfigure}[b]{\textwidth}
  \centering
    \includegraphics[width=0.48\textwidth]{baseSeries/cd_cdr_MF02_divvy.png}
    \includegraphics[width=0.49\textwidth]{baseSeries/err_breakdown_MF02.png}
    \vspace{-0.5\baselineskip}
    \caption{MF$_2$ ($10\%$ HF)}
    \vspace{0.8\baselineskip}
  \end{subfigure}
\caption{Element-wise decomposition of error estimate (right) and domain division (left; low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion) for mixed-fidelity models. Since linear nodal basis elements are used, elements in regions where the high-fidelity model is already being used do not contribute to the error estimate, except for some elements near the boundaries between low-fidelity and high-fidelity regions.}
\label{fig:baseRef}
\end{figure}

@@

\subsection{Constant vs Field Parameters}

\subsection{Cost Comparison}

\subsubsection{Simple Cost Analysis}

Consider a situation like that described in Section \ref{sec:cdvcdr}, where the state, adjoint, and parameter variables each have $N$ degrees of freedom. Suppose the low-fidelity model is linear, so that the cost of solving the inverse problem with the low-fidelity model (or with a mixed-fidelity model that is low-fidelity in most of the domain), is on the order of $(3N)^g$, where $g$ depends on the linear solver used. The cost for computing the auxiliary variables is also on the order of $(3N)^g$, and the cost for computing the supplementary adjoint is on the order of $(6N)^g$. Thus for $T$ iterations of the adaptive algorithm (where $T=1$ if one only calculates the error estimate relative to the low-fidelity model), the cost of using the adaptive algorithm is $T(2+2^g)(3N)^g$.

Suppose the inverse problem with the high-fidelity model is sufficiently nonlinear that a good initial guess is needed for convergence; one way to approach this is to use arclength continuation, a standard procedure in commercial nonlinear finite element programs.\footnote{According to Wikipedia...should see if we can confirm this elsewhere...} Letting $L_i$ represent the number of non-linear iterations required at each continuation step, the cost of solving the inverse problem with the high-fidelity model is $\sum_i L_i (3N)^g$. Assuming that the costs of both the high-fidelity inverse problem and adaptive algorithm are dominated by the cost of the linear solves, it is less costly to use Algorithm \ref{alg:refSeries} when $T<(2+2^g)^{-1}\sum_i L_i$. The bound on $T$ is strictest when $g=3$, as in the case where Gaussian elimination is used, giving $T<\frac{1}{10}\sum_i L_i$.

\subsubsection{Cost Comparison Example}

Here we consider the same problem as in Section \ref{sec:cdvcdr}, but with a reaction term $k_r=-616$ in the high-fidelity model. This reaction term is large enough that if the Newton solver will not converge with a zero initial guess. We first solve the inverse problem with the low-fidelity model ($k_r=0$), and then use the natural continuation approach, using the solution at one value of $k_r$ as the initial guess for the next.\footnote{NOT arclength continuation, which is more difficult to implement, though libMesh appears to have a class for such continuation, which we can use if this seems like a viable direction...}, We increase the reaction term in increments of $\Delta k_r=100$, and halve the increment each time the step is too large (Newton solver does not converge at the next $k_r$ value). From $k_r=0$ to $k_r=-616$, this results in 9 continuation steps being taken, with $\sum_i L_i=30$ linear solves of $N\times N$ systems required.

Since the low-fidelity model is linear in this case, solving for the primary and auxiliary variables takes one linear solve of an $N\times N$ system each. The error estimate is then used to choose $10\%$ of the domain in which to use the high-fidelity model. For this amount of refinement, the estimated relative error is $<1\%$; estimating the error requires five $N\times N$ linear solves for the primary variables and one linear $N\times N$ solve for the auxiliary variables. If adaption stops at this point, then the adaptive algorithm will have required $8+2(2^g)$ solves of $N\times N$ systems. For $g=3$ (Gaussian elimination), this amounts to 24 solves; with iterative methods where $g<3$, this number is smaller.

%does B+V's method for 'cheaply' getting auxiliary variables not really work when parameters are a field and not handful of scalars? does it even matter, since bulk of costs seem to be going to super-adjoint?
